Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
Review abstract -conclusion

\author{
% 1st. author
\alignauthor
John Burchell\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{william.granli@gmail.com}
\and
% 3rd. author
\alignauthor Imed Hammouda\titlenote{Co-author}\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{imed.hammouda@gu.se}
% 4th 
\alignauthor Eric Knauss\titlenote{Co-author}\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{imed.hammouda@gu.se}
}

@@

\textbf{Background  } 
Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored. Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Types of Software Evolution and Software Maintenance and Lehman's laws of software evolution.

\smallskip \noindent
\textbf{Objective  } 
This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view. The aim was also to test how well we could reverse engineer these change decisions. The goal was to study these factors by relating them to existing software evolution theories.

\smallskip \noindent
\textbf{Method  }
This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interviewing the architects of the API. The changes were analysed from a qualitative and investigative point of view.

\smallskip \noindent
\textbf{Results  }
This study identified 13 majors changes to the API. The study concluded that the most major driving force for the evolution of APIs is the drive for new functionality and that change decisions to a large extent can be reverse engineered. It was also found that 7 out of 8 of Lehman's laws were applicable to APIs.

>>>>

\author{
% 1st. author
\alignauthor
John Burchell\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{william.granli@gmail.com}
\and
% 3rd. author
\alignauthor Imed Hammouda\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{imed.hammouda@gu.se}
% 4th 
\alignauthor Er ic Knauss\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{imed.hammouda@gu.se}
}

@@

\textbf{Background  } %Done
The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored. Previous studies have not considered APIs from the perspective of well-established software evolution theories.

\smallskip \noindent
\textbf{Objective  } %Done
In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'. We also aim to evaluate to what extent we are able to reverse engineer these evolutionary change decisions. The goal is to study these factors by evaluating them against existing software evolution theories.

\smallskip \noindent
\textbf{Method  } %Done
This case study was conducted by analysing the changes between two versions of a platform API and its documentation. The results were analysed from a qualitative and investigative perspective, and were then reviewed and validated with the architects of the API.

\smallskip \noindent
\textbf{Results  } %Done
We identified thirteen major changes which were introduced in the new version of the API. We concluded that the dominant driving force of the API evolution is demand for new functionality and that change decisions, to a large extent, are reverse engineerable. We also found that long-established software evolution laws were largely applicable to APIs.
